---
title: "Two Parameters"
author: "Rajeev Kumar Yadav"
format: html
execute: 
  echo: false
---

```{r}
#| label: setup
#| message: false

library(tidyverse)
library(primer.data)
library(brms)
library(tidybayes)
library(gtsummary)
```

Using The nhanes data set from the National Health and Nutrition Examination Survey conducted from 2009 to 2011 by the Centers for Disease Control and Prevention includes 15 variables, including physical attributes like weight and height, we seek to create a model of height for adult men. In particular, what is the average height of an adult male in America in 2024? Since participation in the survey is voluntary, it could mean that, for example, taller men are more likely to answer this question. We modeled height using an intercept-only regression.The average height of adult men in America in 2024 is 176 cm, with standard deviation of 7.48 cm.

```{r}
nhanes |> filter(sex == "Male", age >= 18) |> select(height) |> drop_na() |> ggplot(aes(x = height)) + 
geom_histogram(bins = 50) +
labs(title = "Male Adult Height in the US in 2010",
x = "Height(cm)", caption = "Source: National Health and Nutrition Examination Survey",
y = "Count")
```



```{r}
#| cache: true

ch5 <- nhanes |>
  filter(sex == "Male", age >= 18) |>
  select(height) |>
  drop_na()
fit_male_height <- brm(formula = height ~ 1, data = ch5, family = gaussian(), silent = 2, refresh = 0, seed = )
```

```{r}

tbl_regression(fit_male_height, intercept = TRUE)
```


```{r}
#| label: plot

ndata <- tibble(.rows = 1)
fit_male_height |> 
add_predicted_draws(newdata = ndata) |>
ggplot(aes(x = .prediction)) +
geom_histogram(aes(y = after_stat(count/sum(count))), bins = 100) +
labs(title = "Posterior for Height of Random Male",
         subtitle = "Uncertainty for a single individual is much greater than for the expected value",
         x = "Height (cm)",
         y = "Probability",
         caption = "Data source: NHANES") +
scale_x_continuous(labels = scales::number_format()) +
scale_y_continuous(labels = scales::percent_format(accuracy = 1))
```

```{r}

fit_male_height |> add_predicted_draws(newdata = ndata) |>
mutate(tall = if_else(.prediction > 180, TRUE, FALSE)) |>
summarize(odds = mean(tall))
```

